The Astropy Project

### 2017-11-13 main.tex
package

The \package{visualization} package provides functionality that can be helpful when visualizing data. This includes a framework for plotting astronomical images with coordinates with Matplotlib (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for Matplotlib.

>>>>

The \package{astropy.visualization} subpackage provides functionality that can be helpful when visualizing data. This includes a framework for plotting astronomical images with coordinates with \package{matplotlib} (previously the standalone \package{wcsaxes} package), functionality related to image normalization (including both scaling and stretching), smart histogram plotting, RGB color image creation from separate images, and custom plotting styles for \package{matplotlib}.
